---
title: "A Study Based on Demographics of 99 Iowa Counties"
date: "2018-12-07T21:49:57-07:00"
categories:
  - Products
tags:
  - Statistics 
  - Data 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


![](https://upload.wikimedia.org/wikipedia/commons/f/fc/Blank_Iowa_county_map_with_county_names.svg)


## Load Packages
In order to accomplish these following tasks: 

* Data manipulation
* Correlation
* Histogram Visualization
* 2-sample t test

I use the these following packages in R:
```{r , results='hide', message=FALSE }
library(dplyr)
library(magrittr)
library(ggplot2)
library(ggpubr)
library(psych)
library(Hmisc)
library(devtools)
```

## Import Data
I used a .csv file to store all collected data from the U.S. Census. My target are 99 counties of the state of Iowa.

```{r}
my_data <- read.csv("/Users/yiwenw/Desktop/741 data/Iowa.csv", header=TRUE, stringsAsFactors=FALSE)
```



## Check Variables 
By using `head`, we are able to check all variables collected for future data analysis. From U.S. Census Data, I collected the following data as my variables: data2010 population, 2017 population, number of bachelor obtained for over 25 year-old, population count that is below poverty, mean of income, and the median house value

```{r}
head(my_data)
```

## Univariate Statistics 
By running `summary`, we are able to learn some basic statistics of our dataset. These statistics are range, mean and median.

```{r}
summary(my_data)
```



### Histograms and Density Distributions


```{r}
x <- my_data$mean.income
hist(x,main = "Distribution of Mean of Income", xlab = "Income Range", 
     col = "blue", border ="black", prob = T )
lines(density(x, adjust = 2), col = "red")

```

```{r}
y <- my_data$median.house
hist(y,main = "Distribution of Median House Value", xlab = "Value Range", 
     xlim = c(0, 220000), col = "blue", border ="black", prob=TRUE)
lines(density(y, adjust = 2), col = "red")

```

Based on the population size, I devide 99 counties into three tiers of counties.
1. Population between 3600 and 11000: 33 counties -pop1
2. Population between 11000 and 20000: 33 counties - pop2
3. Population between 20000 and 482000: 33 counties - pop3





```{r}
pop1 <- filter(my_data, by.pop == 1)
y1 <- pop1$mean.income
hist(y1,main = "Income Distribution with Lower 1/3 House Values", xlab = "Income Range", 
     xlim = c(60000, 150000), col = "blue", border ="black", prob=TRUE)
lines(density(y1, adjust = 2), col = "red")

```
```{r}
head(y1)
```
```{r}
head(pop1)
```



```{r}
pop2 <- filter(my_data, by.pop == 2)
y2 <- pop2$mean.income
hist(y2,main = "Income Distribution with Middle 1/3 House Values", xlab = "Income Range", 
     xlim = c(60000, 150000), col = "blue", border ="black", prob=TRUE)
lines(density(y2, adjust = 2), col = "red")

```


```{r}
pop3 <- filter(my_data, by.pop == 3)
y3 <- pop3$mean.income
hist(y3,main = "Income Distribution with Top 1/3 House Values", xlab = "Income Range", 
     xlim = c(60000, 150000), col = "blue", border ="black", prob=TRUE)
lines(density(y3, adjust = 2), col = "red")

```


#### Correlation between number of bachelor over 25 in age and number under poverty
Normally, we would expact the correlation between number of bechalor degrees obtained and the number of people under poverty. However, the truth can be: the more bechalors a county has, the bigger population it may have. Therefore, it is more likely to have more people under poverty.

```{r}
correlation1 <- cor(my_data$Over25.Bach, my_data$below.poverty, 
                   method = c("pearson"))
correlation1

```
#### Correlation between median house value and mean of income.
There is a strong positive correlation between median house value and the average income. 

```{r}
correlation2 <- cor(my_data$median.house, my_data$mean.income, 
                    method = c("pearson"))
correlation2

```

#### Correlation between number of employed and mean of income.
It is very likely that there is no correlation between number of employed and the mean of income.

```{r}
correlation3 <- cor(my_data$employed, my_data$mean.income, 
                    method = c("pearson"))
correlation3

```

#### Correlation between number of employed and number under poverty.
It is very likely that there is no correlation between number of employed and the number under poverty
```{r}
correlation4 <- cor(my_data$employed, my_data$below.poverty, 
                    method = c("pearson"))
correlation4

```


##T- test

```{r}
res <- t.test(my_data$pop.2017, my_data$mean.income, data = my_data, var.equal = TRUE)
res

```
